### 2011-06-20 standing-patches-paper.tex
/* The Next Paper */ rearranged the discrete section

\section{Patchy selection}

\subsection{Model}

In this section, we will relax the assumption that the uniform is homogenous.
The model we analyze in section \ref{ss:discretedemes} is a model of discrete demes exchanging rare migrants,
but since the object of this paper is to work in continuous space,
we will first in sections \ref{ss:patchymutation} and \ref{ss:patchymigration} describe how a model with {\em patchy} selection can be approximated by such a discrete model.

For this purpose, suppose that instead of a uniform habitat,
the selective pressure is such that the new alleles are only advantageous in isolated locations, 
and are disadvantageous in the intervening region.
As before, we assume that the new allele has fitness $1+s_b$ relative to the unmutated type in the ``good'' patches,
and assume that it has fitness $1+s_m$ in the intervening areas, with $s_m<0$.
To make things tractable, we assume that the distances between the patches are large relative to migration distance $\sigma$,
and that the disadvantage $s_m$ ensures that on the relevant timescale,
the allele is very unlikely to fix locally in the regions where it is at a disadvantage.
With these assumptions as justification, we will move to a model of discrete demes exchanging migrants,
where ``migration'' occurs through the rare, transient passage of the new allele through regions where it is disadvantageous.

\subsection{Mutational influx}
\label{ss:patchymutation}

\subsection{Migration rates}
\label{ss:patchymigration}

\subsection{Discrete populations}
\label{ss:discretedemes}

@@

@@

>>>>

\section{Patchy selection} 
\label{ss:discretedemes}

We have been working in a continuous model of geographic space; 
in this section we move to a discrete model of isolated populations exchanging rare migrants,
but in section \ref{ss:patchyspace} discuss how a model with {\em patchy} selection can be approximated by such a discrete model.

@@

\subsection{Symmetric patches}

@@

\subsection{Relation to a continuous model
\label{ss:patchyspace}

A similar situation of interest is the case when the species occupies a continuous range, but the selective pressure itself is patchy.
If the areas where the new allele is advantageous are relatively isolated,
we might hope to apply the results above to such a situation.
For this purpose, suppose that instead of a uniform habitat,
the selective pressure is such that the new alleles are only advantageous in isolated locations, 
and are disadvantageous in the intervening region.
As before, we assume that the new allele has fitness $1+s_b$ relative to the unmutated type in the ``good'' patches,
and assume that it has fitness $1+s_m$ in the intervening areas, with $s_m<0$.
To make things tractable, we assume that the distances between the patches are large relative to migration distance $\sigma$,
and that the disadvantage $s_m$ ensures that on the relevant timescale,
the allele is very unlikely to fix locally in the regions where it is at a disadvantage.
With these assumptions as justification, we will move to a model of discrete demes exchanging migrants,
where ``migration'' occurs through the rare, transient passage of the new allele through regions where it is disadvantageous.

\subsubsection{Mutational influx}
\label{ss:patchymutation}

\subsubsection{Migration rates}
\label{ss:patchymigration}
